\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}

First and foremost, I would like to express my deepest gratitude to the Almighty for giving me the strength, health, and patience to successfully complete my industrial attachment and write this report.

I express my heartfelt gratitude and sincere thanks to my industry supervisor, \textbf{[Supervisor's Name]}, [Supervisor's Designation] at \textbf{Texlab IT}, Rajshahi, for their invaluable guidance, constant encouragement, constructive feedback, and active support throughout my internship period. I also extend my gratitude to the management of Texlab IT for providing me with the opportunity to undertake my training in such a collaborative and professional work environment.

I would also like to thank all the instructors, trainers, and software engineers at Texlab IT who shared their technical expertise and industrial experience, helping me bridge the gap between academic theory and industry practice. Their support in troubleshooting issues related to database scalability, containerization, and backend integration was immensely helpful.

Additionally, I would like to express my sincere appreciation to the Department of Computer Science and Engineering at \textbf{[Your University Name]} for facilitating this industrial attachment. I am grateful to our department head, teachers, and internship coordinators for their continuous guidance and academic supervision.

Finally, I am deeply indebted to my family and peers for their moral support, understanding, and encouragement during the course of my studies and training.

\vspace{1.5cm}

\noindent
\textbf{Md. Azmain Yakin Srizon}
