\chapter{Organization Overview}

\section{History and Mission}
\textbf{Texlab IT} is a well-established IT training provider and software services agency located in Rajshahi, Bangladesh. Founded in 2015, the organization was created to address a critical local need: bridging the digital divide by equipping youth, students, and professionals in the Rajshahi region with high-demand technical skills. Over the past decade, Rajshahi has emerged as an aspiring technology hub in Bangladesh, and Texlab IT has been at the forefront of this transformation.

The mission of Texlab IT is to provide practical, employment-focused IT training and deliver high-quality web engineering solutions to international and local markets. By offering courses in modern technologies and engaging in custom software development, Texlab IT seeks to cultivate a pool of competent developers, graphic designers, and digital marketers capable of competing in global freelancing and software outsourcing markets.

\section{Organizational Structure}
Texlab IT operates under a hierarchical yet collaborative management model that ensures smooth cooperation between training, development, and administration. The structure is outlined below:
\begin{enumerate}
    \item \textbf{Executive Management:} Consists of the CEO and Managing Director, who oversee strategic partnerships, financial planning, and company expansion.
    \item \textbf{Software Development & Digital Agency Division:} Responsible for custom client projects, software engineering, quality assurance, and technical support.
    \item \textbf{Training & Mentorship Division:} Handles syllabus creation, teaching professional courses, guiding lab exercises, and providing student career counseling.
    \item \textbf{Marketing & Client Relations Division:} Manages client acquisition, brand outreach, local student enrollment, and international freelancing account management.
    \item \textbf{Human Resources & Administration:} Manages hiring, onboarding, intern training programs, office administration, and payroll.
\end{enumerate}

\section{Departments and Functions}
To support its dual mission of software development and IT training, Texlab IT is structured into several functional departments:

\subsection{Software Engineering Department}
The Software Engineering Department is where production client applications are designed, built, and maintained. The department utilizes modern technology stacks, primarily PHP/Laravel, Node.js, and increasingly Go (Golang) for high-performance microservices and API gateways. Software engineers collaborate using agile workflows, organizing tasks into sprints, and using version control repositories (GitHub/GitLab) for code reviews and continuous integration.

\subsection{Training Department}
The Training Department is responsible for designing and delivering skill development courses. Their offerings include:
\begin{itemize}
    \item Front-End Web Design (HTML5, CSS3, JavaScript, Bootstrap, Tailwind CSS).
    \item Full-Stack Web Development (React, Node.js, PHP, MySQL, WordPress).
    \item Graphic Design and UI/UX prototyping.
    \item Search Engine Optimization (SEO) and Digital Marketing.
\end{itemize}
This department features computer labs equipped with modern workstations where students and interns carry out lab assignments under the supervision of industry mentors.

\subsection{Quality Assurance (QA) & Support Department}
The QA team ensures that software delivered to clients meets strict functional and security requirements. They perform manual functional testing, regression testing, and interface validation, ensuring cross-browser compatibility and mobile responsiveness.

\section{Products and Services}
Texlab IT offers a range of services to domestic and international clients, including:
\begin{itemize}
    \item \textbf{Custom Web Application Development:} Developing secure, scalable web systems such as e-commerce platforms, educational portals, and content management systems.
    \item \textbf{IT Training and Certification:} Providing structured technical training programs with physical certificates, helping students transition to professional web roles.
    \item \textbf{Digital Agency Services:} Helping local businesses build their digital presence through UI/UX design, SEO, social media marketing, and branding services.
\end{itemize}

\section{Quality and Compliance Standards}
To maintain the quality of both its training and software deliverables, Texlab IT complies with standard software development guidelines:
\begin{itemize}
    \item \textbf{Version Control & Code Reviews:} Every feature branch must be peer-reviewed before being merged into the master or production branches.
    \item \textbf{Secure Coding Guidelines:} Following OWASP Top 10 recommendations to prevent vulnerabilities like SQL injection, Cross-Site Scripting (XSS), and Broken Authentication.
    \item \textbf{Agile Project Management:} Using tools like Trello or Jira to track tasks, log bugs, and monitor project development speed.
\end{itemize}

\section{Workplace Safety and Environmental Policy}
Texlab IT maintains a safe and comfortable environment for employees, trainees, and interns:
\begin{itemize}
    \item \textbf{Workplace Safety:} The office features an open-space layout with ergonomic seating, adequate lighting, air conditioning, and fire safety equipment (extinguishers). A strict compliance with local safety regulations is maintained.
    \item \textbf{Environmental Responsibility:} The organization takes active steps to minimize its carbon footprint by using energy-efficient LED lighting, configuring computing hardware to enter low-power sleep states when idle, and encouraging paperless administrative workflows (using cloud-based document sharing rather than printing).
    \item \textbf{Flexibility:} To maintain worker well-being, employees and interns are provided with remote-work flexibility when needed, reducing travel emissions and promoting work-life balance.
\end{itemize}
